Postural developments mediate children's visual access to social information

### 2018-01-30 writeup-cogsci/cogsci2018_faceOnly_alessandro.Rmd
< six pages!

all_subs %>%
  left_join(inc_subs) %>%
  group_by(age_group) %>%
  summarise(n = sum(inc), 
            percent_included = mean(inc),
            age = mean(age.at.test, na.rm=TRUE), 
            video_length = mean(len.min, na.rm=TRUE), 
            female = sum(gender=="female", na.rm=TRUE)) %>%
  xtable %>%
  print(digits = 2, include.rownames=FALSE,table.placement = "H", type="latex", comment = F)
```

Our final sample consisted of 36 infants and children, with 12 participants in three age groups: 8 months (6 F), 12 months (7 F), and 16 months (6 F). Participants were recruited from the surrounding community via state birth records, had no documented disabilities, and were reported to hear at least 80\% English at home. Demographics and exclusion rates are given in Table \ref{tab:pop}.  
\begin{table}[ht]
\centering
\begin{tabular}{rrrrrr}
  \hline
 Group & N & \% incl. & Avg age & Avg video length (min) \\ 
  \hline
   8 mo. &   12 & 0.46 & 8.71 & 14.41 \\ 
   12 mo. &  12 & 0.40 & 12.62 & 13.48 \\ 
   16 mo. &  12 & 0.31 & 16.29 & 15.00\\ 
   \hline
\end{tabular}
\caption{\label{tab:pop} Demographics by age group.}
\end{table}
To obtain this final sample, we tested `r length(all_subs$reason)` children, excluding  `r sum(all_subs$reason!="included")` children for the following reasons:
`r sum(all_subs$reason=="HC technical error")` for technical issues related to the headcam,
`r sum(all_subs$reason=="would not wear camera")` for failing to wear the headcam,
`r sum(all_subs$reason=="less than 4 min HC footage")` for fewer than 4 minutes of headcam footage,
`r sum(all_subs$reason=="multiple people")` for having multiple adults present,
`r sum(all_subs$reason=="no CDI")` for missing Communicative Development Inventory (CDI) data,
`r sum(all_subs$reason=="no DV cam footage")` for missing scene camera footage,
`r sum(all_subs$reason=="infant crying")` for fussiness, and one for sample symmetry. All inclusion decisions were made independent of the results of subsequent analyses. Some of these data were also analyzed in @frank2013.

@@

### Procedure
All parents signed consent documents while children were fitted with the headcam. If the child was uninterested in wearing the headcam or tried to take it off, the experimenter presented engaging toys to try to draw the child's focus away from the headcam [@yoshida2008]. When the child was comfortable wearing the headcam, the child and caregiver were shown to a playroom for the free-play session. Parents were shown a box containing three pairs of novel and familiar objects (e.g., a ball and a microfiber duster, named a "zem"), and were instructed to play with the object pairs with their child one at a time, "as they typically would." All parents confirmed that their child had not previously seen the novel toys and were instructed to use the novel labels to refer to the novel toys. The experimenter then left the playroom for approximately 15 minutes, during which a tripod-mounted camera in the corner of the room recorded the session and the headcam captured video from the child's perspective.

@@

\begin{table}[H]
\centering
\begin{tabular}{rrrrr}
  \hline
 & Estimate & Std. Error & z value & Pr($>$$|$z$|$) \\ 
  \hline
  \textbf{Faces} \\
  Intercept & -5.2469 & 0.0584 & -89.88 & 0.0000 \\ 
  Age & 0.0847 & 0.0041 & 20.89 & 0.0000 \\ 
  Prone & 0.2015 & 0.0564 & 3.57 & 0.0004 \\ 
  Sit & 1.4053 & 0.0541 & 25.98 & 0.0000 \\ 
  Stand & 1.4272 & 0.0542 & 26.33 & 0.0000 \\ 
  Close & 1.8239 & 0.0230 & 79.17 & 0.0000 \\ 
  Far & 2.5479 & 0.0239 & 106.42 & 0.0000 \\ 
  \hline
  & Estimate & Std. Error & z value & Pr($>$$|$z$|$) \\ 
  \hline
  \textbf{Wrists} \\ 
  Intercept & -5.0818 & 0.0776 & -65.46 & 0.0000 \\ 
  Age & 0.0564 & 0.0050 & 11.35 & 0.0000 \\ 
  Prone & 0.9499 & 0.0774 & 12.27 & 0.0000 \\ 
  Sit & 1.7282 & 0.0758 & 22.79 & 0.0000 \\ 
  Stand & 1.6618 & 0.0760 & 21.88 & 0.0000 \\ 
  Close & 0.7472 & 0.0188 & 39.81 & 0.0000 \\ 
  Far & 1.6357 & 0.0200 & 81.61 & 0.0000 \\ 
   \hline
\end{tabular}
\caption{Model coefficients from generalized linear models predicting the proportion of faces (upper panel) and wrists (lower panel) seen by children.} 
\end{table}

To formalize these observations, we fit a generalized linear model to the proportion of faces infants saw in each posture and orientation (as detected by MTCNN), with participant's age, orientation, and posture as independent variables. A summary of the coefficients of a model with only main effects (and no interactions) can be found in Table 3.  When we did include interaction terms between age, posture, and orientation, age no longer remained a significant predictor (b = `r round(faceGLMOut$coef[2,1],2)`, SE = `r round(faceGLMOut$coef[2,2],2)`, z = `r round(faceGLMOut$coef[2,3],2)` , p = `r round(faceGLMOut$coef[2,4],2)`). We also found the same pattern with respect to infants' visual access to hands (see Table 3); including interaction terms also eliminated any main effect of age on the proportion of wrists detected (b = `r round(wristGLMOut$coef[2,1],2)`, SE = `r round(wristGLMOut$coef[2,2],2)`, z = `r round(wristGLMOut$coef[2,3],2)`, p = `r round(wristGLMOut$coef[2,4],2)`). Thus, these results suggest that infants' visual access to social information is mediated by their posture and orientation, which is in turn a function of their general locomotor development (as indexed by chronological age).

>>>>

all_subs %>%
  left_join(inc_subs) %>%
  group_by(age_group) %>%
  summarise(n = sum(inc), 
            percent_included = mean(inc),
            age = mean(age.at.test, na.rm=TRUE), 
            video_length = mean(len.min, na.rm=TRUE), 
            female = sum(gender=="female", na.rm=TRUE)) %>%
  xtable %>%
  print(digits = 2, include.rownames=FALSE,table.placement = "H", type="latex", comment = F)

# <!-- \caption{\label{tab:pop} Demographics by age group.} -->
```

Our final sample consisted of 36 infants and children, with 12 participants in three age groups: 8 months (6 F), 12 months (7 F), and 16 months (6 F). Participants were recruited from the surrounding community via state birth records, had no documented disabilities, and were reported to hear at least 80\% English at home. Demographics and exclusion rates are given in the table below.
\begin{table}[ht]
\centering
\begin{tabular}{rrrrrr}
  \hline
 Group & N & \% incl. & Avg age & Avg video length (min) \\ 
  \hline
   8 mo. &   12 & 0.46 & 8.71 & 14.41 \\ 
   12 mo. &  12 & 0.40 & 12.62 & 13.48 \\ 
   16 mo. &  12 & 0.31 & 16.29 & 15.00\\ 
   \hline
\end{tabular}
\end{table}
To obtain this final sample, we tested `r length(all_subs$reason)` children, excluding  `r sum(all_subs$reason!="included")` children for the following reasons:
`r sum(all_subs$reason=="HC technical error")` for technical issues related to the headcam,
`r sum(all_subs$reason=="would not wear camera")` for failing to wear the headcam,
`r sum(all_subs$reason=="less than 4 min HC footage")` for fewer than 4 minutes of headcam footage,
`r sum(all_subs$reason=="multiple people")` for having multiple adults present,
`r sum(all_subs$reason=="no CDI")` for missing Communicative Development Inventory (CDI) data,
`r sum(all_subs$reason=="no DV cam footage")` for missing scene camera footage,
`r sum(all_subs$reason=="infant crying")` for fussiness, and one for sample symmetry. All inclusion decisions were made independent of the results of subsequent analyses. Some of these data were also analyzed in @frank2013.

@@

### Procedure
All parents signed consent documents while children were fitted with the headcam. If the child was uninterested in wearing the headcam or tried to take it off, the experimenter presented engaging toys to try to draw the child's focus away from the headcam. When the child was comfortable wearing the headcam, the child and caregiver were shown to a playroom for the free-play session. Parents were shown a box containing three pairs of novel and familiar objects (e.g., a ball and a microfiber duster, named a "zem"), and were instructed to play with the object pairs with their child one at a time, "as they typically would." All parents confirmed that their child had not previously seen the novel toys and were instructed to use the novel labels to refer to the novel toys. The experimenter then left the playroom for approximately 15 minutes, during which a tripod-mounted camera in the corner of the room recorded the session and the headcam captured video from the child's perspective.

@@

```
To formalize these observations, we fit a generalized linear model to the proportion of faces infants saw in each posture and orientation (as detected by MTCNN), with participant's age, orientation, and posture as independent variables. 
\begin{table}[H]
\centering
\begin{tabular}{rrrrr}
  \hline
 & Estimate & Std. Error & z value & Pr($>$$|$z$|$) \\ 
  \hline
  \textbf{Faces} \\
  Intercept & -5.2469 & 0.0584 & -89.88 & 0.0000 \\ 
  Age & 0.0847 & 0.0041 & 20.89 & 0.0000 \\ 
  Prone & 0.2015 & 0.0564 & 3.57 & 0.0004 \\ 
  Sit & 1.4053 & 0.0541 & 25.98 & 0.0000 \\ 
  Stand & 1.4272 & 0.0542 & 26.33 & 0.0000 \\ 
  Close & 1.8239 & 0.0230 & 79.17 & 0.0000 \\ 
  Far & 2.5479 & 0.0239 & 106.42 & 0.0000 \\ 
  \hline
  & Estimate & Std. Error & z value & Pr($>$$|$z$|$) \\ 
  \hline
  \textbf{Wrists} \\ 
  Intercept & -5.0818 & 0.0776 & -65.46 & 0.0000 \\ 
  Age & 0.0564 & 0.0050 & 11.35 & 0.0000 \\ 
  Prone & 0.9499 & 0.0774 & 12.27 & 0.0000 \\ 
  Sit & 1.7282 & 0.0758 & 22.79 & 0.0000 \\ 
  Stand & 1.6618 & 0.0760 & 21.88 & 0.0000 \\ 
  Close & 0.7472 & 0.0188 & 39.81 & 0.0000 \\ 
  Far & 1.6357 & 0.0200 & 81.61 & 0.0000 \\ 
   \hline
\end{tabular}
\caption{Model coefficients from generalized linear models predicting the proportion of faces (upper panel) and wrists (lower panel) seen by children.} 
\end{table}

A summary of the coefficients of a model with only main effects (and no interactions) can be found in Table 2.  When we did include interaction terms between age, posture, and orientation, age no longer remained a significant predictor (b = `r round(faceGLMOut$coef[2,1],2)`, SE = `r round(faceGLMOut$coef[2,2],2)`, z = `r round(faceGLMOut$coef[2,3],2)` , p = `r round(faceGLMOut$coef[2,4],2)`). We also found the same pattern with respect to infants' visual access to hands (see Table 3); including interaction terms also eliminated any main effect of age on the proportion of wrists detected (b = `r round(wristGLMOut$coef[2,1],2)`, SE = `r round(wristGLMOut$coef[2,2],2)`, z = `r round(wristGLMOut$coef[2,3],2)`, p = `r round(wristGLMOut$coef[2,4],2)`). Thus, these results suggest that infants' visual access to social information is mediated by their posture and orientation, which is in turn a function of their general locomotor development.
